Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-19 paper/main.tex
second page ready

\hl{redukcja i bridge pomiedzy intro (usunac subsection)}

co to jest jump flooding? tak naprawde to nie jest algorytm do voronoi-a tylko
pattern komunikacyjny w programowaniu rownoleglym - swojej pracy doktorskiej
autor tej techniki podaje wiele zastosowan jednak w swoich badaniach ogranicza
sie do Voronoi-a. glownym pytaniem roznych takich patternow jest ile potrzebnych
jest rund/operacji komunikacji aby zagwarantowac aby dana informacja zostanie
dostarczona. akurat w voronoi-u wiele komorek jest lokalna w skali calego
przykladu - wiec JFA ktora gwarantuje dostarczenie informacji globalnie do
kazdego punktu - wykonuje pewne niepotrzebne operacje.  szybkosc i zajetosc
pamieciowa JFA jest satysfakcujaca, jednak proste modyfikacje pokazuja ze
algorytm ten wykonuje sie szybciej w pewnych przypadkach (i to typowych).
dlatego naturalnym pytanie powinno byc w jakich oraz jakie modyfikacje wplywaja
na szybkosc dzialania.

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & Bruteforce           & Bruteforce        & JFA       \\
High ($\rho$=0.01-0.1)        & JFA           & JFA        & JFA       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{State-of-the-art for specific domains (before our work).}
\end{table}

@@

\begin{figure}[H]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_1_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_1_out}
		,
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_2_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_2_out}
		\caption{Noise for 32x32}
		\label{Fig:noise}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_1_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_1_out}
		,
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_2_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_2_out}
		\caption{Local Noise for 32x32}
		\label{Fig:lnoise}
	\end{minipage}
\end{figure}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & 
	Bruteforce & 
	?          & 
	?          \\
High ($\rho$=0.01-0.1)        & 
	?          &
	?             &
	?          \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

@@

\subsubsection{Small Shape: 32x32, 64x64, 96x96, 128x128}

@@

\subsubsection{Medium Shape: 256x256, 320x320, 384x384, 448x448}
\subsubsection{Large Shape: 512x512, 768x768, 1024x1024, 1536x1536}

>>>>

Algorithm for Voronoi Diagram that uses jump flooding as communication pattern
propagates the information (2D coordinates and ID) of all sites to all the
pixels in the matrix.  It is based on the observation that while flooding an
area with a seed, each seeded pixel can transmit its information, instead of
just the ones on the boundaries of the Voronoi cell.

In each round, the site information stored in each pixel $(x, y)$ is propagated
to at most eight other pixels at $(x+i, x+j)$ where $i,j \in \{-k, 0, k\}$, and
$k$ is the step length of the current round.  In the first round, we use $n/2$
as the initial step length to ensure that each pixel is reached by at least one
site. The step length $k$ is halved in each of the following round.  All pixels
are processed in parallel by the GPU. This ensures an exponential increase in
the number of seeded pixels in a grid and thus, can be flooded in $O(\log n)$
rounds, for an $n \times n$ grid \citep{yuan2011generalized}.

% (JFA) o dowodzie ze log(n)
% (JFA) o zbednych przekazaniach

% [original]
% 
% "Generalized Voronoi Diagram Computation on GPU"
%
% The jump flooding algorithm (JFA) computes a Voronoi
% diagram in a discrete 2D space represented by a 2D texture.
% It propagates the information (2D coordinates and ID) of all
% sites to all the pixels in the texture. In the first stage, called
% mapping stage, each site is mapped to its corresponding
% pixel in the texture. It can be done in parallel by the GPU
% rasterizer. The second stage, flooding stage, consists of log 𝑛
% rounds of flooding, where 𝑛 is the dimension of the texture.
% All pixels are processed in parallel by the GPU. In each
% round, the site information stored in each pixel 𝑝(𝑥, 𝑦) is
% propagated to at most eight other pixels at (𝑥 + 𝑖, 𝑦 + 𝑗)
% where 𝑖, 𝑗 ∈ {−𝑘, 0, 𝑘}, and 𝑘 is the step length of the
% current round. In the first round, we use 𝑛/2 as the initial
% step length to ensure that each pixel is reached by at least
% one site. Here we assume 𝑛 is a power of 2. If not, the initial
% step length is set as 2⌈log 𝑛⌉−1. The step length 𝑘 is halved
% in each of the following round. When more than one sites
% are propagated into the same pixel, the nearest site to the
% pixel will be chosen to update it. After the round with the
% step length of 1, the result is the computed Voronoi diagram.

% [FIXME]
% co to jest jump flooding? tak naprawde to nie jest algorytm do voronoi-a tylko
% pattern komunikacyjny w programowaniu rownoleglym - swojej pracy doktorskiej
% autor tej techniki podaje wiele zastosowan jednak w swoich badaniach ogranicza
% sie do Voronoi-a. glownym pytaniem roznych takich patternow jest ile potrzebnych
% jest rund/operacji komunikacji aby zagwarantowac aby dana informacja zostanie
% dostarczona. akurat w voronoi-u wiele komorek jest lokalna w skali calego
% przykladu - wiec JFA ktora gwarantuje dostarczenie informacji globalnie do
% kazdego punktu - wykonuje pewne niepotrzebne operacje.  szybkosc i zajetosc
% pamieciowa JFA jest satysfakcujaca, jednak proste modyfikacje pokazuja ze
% algorytm ten wykonuje sie szybciej w pewnych przypadkach (i to typowych).
% dlatego naturalnym pytanie powinno byc w jakich oraz jakie modyfikacje wplywaja
% na szybkosc dzialania.

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & Bruteforce           & Bruteforce        & JFA       \\
High ($\rho$=0.01-0.1)        & JFA           & JFA        & JFA       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{State-of-the-art for specific domains (before our work).}
\end{table}

@@

\begin{figure}[H]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_1_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_1_out}
		,
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_2_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_noise_2_out}
		\caption{Noise for $32 \times 32$}
		\label{Fig:noise}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_1_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_1_out}
		,
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_2_in}
		\includegraphics[width=0.23\linewidth]{../figures/mod_lnoise_v2_2_out}
		\caption{Local Noise for $32 \times 32$}
		\label{Fig:lnoise}
	\end{minipage}
\end{figure}

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
    & Small (32-128$\times$)
	& Medium (256-448$\times$)
	& Large (512-1536$\times$)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & 
	Bruteforce & 
	?          & 
	?          \\
High ($\rho$=0.01-0.1)        & 
	?          &
	?             &
	?          \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

@@

\subsubsection{Small Shape: $32\times32$, $64\times64$, $96\times96$, $128\times128$}

@@

\subsubsection{Medium Shape: $256\times256$, $320\times320$, $384\times384$, $448\times448$}
\subsubsection{Large Shape: $512\times512$, $768\times768$, $1024\times1024$, $1536\times1536$}
